\chapter{Introduction}
\label{chap:introduction}
\setlength{\parskip}{1em}

The fourth industrial revolution, commonly known as Industry 4.0, is fundamentally transforming manufacturing processes through the integration of digital technologies, artificial intelligence, and interconnected sensor networks. This digital transformation presents unprecedented opportunities for optimizing industrial operations, particularly in the crucial area of equipment maintenance and reliability. As manufacturing facilities become increasingly automated and data-driven, the ability to predict and prevent equipment failures has emerged as a critical factor in maintaining operational efficiency and reducing costly unplanned downtime.

In Kazakhstan's industrial sector, particularly within major operations like Eurasian Resources Group (ERG), the transition toward predictive maintenance represents a significant opportunity for operational improvement. Traditional maintenance approaches, based on fixed schedules or reactive responses to failures, are increasingly inadequate in modern manufacturing environments where equipment downtime can result in substantial financial losses. The abundance of sensor data from industrial equipment, combined with advances in machine learning technologies, creates the potential for more sophisticated maintenance strategies.

Recent developments in artificial intelligence and machine learning have revolutionized the approach to time-series analysis and anomaly detection in industrial settings. Various architectural approaches have shown promising results in processing and analyzing temporal data from industrial sensors. Recurrent Neural Networks (RNNs) \cite{waqas-2024-critical} have demonstrated capability in handling sequential data, while Long Short-Term Memory (LSTM) \cite{van-houdt-2020} networks have proven particularly effective in capturing long-term dependencies in time series data. Convolutional Neural Networks (CNNs) \cite{oshea-2015}, traditionally associated with image processing, have shown surprising efficacy in temporal pattern recognition when applied to sensor data. More recently, Transformer models \cite{ashish2017attention}, with their attention mechanisms, have emerged as powerful tools for processing sequential data, offering potential advantages in capturing complex relationships in industrial time series.

However, the current landscape of predictive maintenance solutions presents several challenges. Many existing systems are proprietary, requiring significant investment and creating vendor dependency. These closed-source solutions often operate as "black boxes," making it difficult for industrial engineers to understand, validate, or customize the systems according to their specific needs. This lack of transparency can lead to hesitation in adoption and challenges in implementation, particularly in critical industrial processes where understanding system behavior is crucial for safety and reliability.

Our research addresses these challenges by developing an open-source, transparent solution for predictive maintenance in industrial settings. By focusing on the specific context of metallurgical operations in Kazakhstan, particularly ERG's thermal-ore furnaces in Aksu, we aim to create a system that is both effective and accessible. The solution leverages existing industrial infrastructure, including AVEVA Historian and SQL Server, while implementing advanced machine learning techniques for predictive analysis.

The significance of this work extends beyond immediate operational improvements. By creating an open-source solution, we aim to contribute to the broader development of Kazakhstan's industrial sector, providing a framework that can be adapted and improved by the industrial community. This approach aligns with the growing need for transparent, customizable solutions in industrial automation while addressing the practical challenges of implementing predictive maintenance in real-world manufacturing environments.

This research combines theoretical advancement in machine learning with practical industrial application, focusing on developing solutions that are not only technically sophisticated but also practically implementable in industrial settings. Through this work, we aim to demonstrate how open-source predictive maintenance solutions can provide a viable alternative to proprietary systems while offering the transparency and flexibility needed in modern industrial operations.

\section{Data from manufacturing facility}
We were able to reach out to "Business \& Technology Services" LLP to learn more about processes at manufacturing facilities of "Eurasian Resources Group" LLP.

\subsection{Facilities in Kazakhstan}

The research work is conducted in collaboration with "Eurasian Resources Group" LLP (ERG), one of Kazakhstan's largest mining and metallurgical companies. ERG operates a diverse portfolio of industrial facilities across the country, including coal mining operations, ferro-alloy production plants, and metal processing facilities. The company's infrastructure encompasses multiple production sites, with operations ranging from open-pit mining to sophisticated metallurgical processes.

ERG's facilities are equipped with extensive Internet of Things (IoT) infrastructure, including numerous sensors, automated control systems, and data collection points throughout their production chain. These devices continuously monitor various parameters such as equipment temperature, vibration levels, power consumption, and production metrics. The existing IoT network generates substantial amounts of operational data, creating a robust foundation for advanced analytics and predictive modeling.

Despite having a modern technological infrastructure, the company currently employs traditional maintenance approaches, primarily relying on scheduled maintenance intervals and reactive repairs when equipment failures occur. The absence of a predictive maintenance system based on forecasting models results in suboptimal resource allocation and potentially preventable equipment downtime. This gap between available data capabilities and maintenance practices presents an opportunity for significant operational improvements.

The company has expressed strong interest in developing and implementing a software solution for predictive maintenance. Such a system would leverage the existing IoT infrastructure and historical operational data to forecast potential equipment failures and optimize maintenance scheduling. This research aims to address this industrial need by developing a comprehensive predictive maintenance framework tailored to ERG's specific operational context and requirements.

The practical significance of this research is underscored by ERG's position as a major industrial player in Kazakhstan's economy and the potential for substantial operational efficiency improvements through the implementation of data-driven maintenance strategies. The company's diverse range of facilities and equipment types also provides an excellent opportunity to develop and validate predictive maintenance models across different industrial contexts.

\subsection{Dataset}

The research utilizes a comprehensive dataset collected from one of Kazakhstan's largest ferrous alloy smelting facilities, located in Aksu, Pavlodar region. The facility operates thermal-ore furnaces, which are crucial components in the metallurgical process of producing ferroalloys. Each furnace is equipped with three graphite electrodes that play a vital role in the smelting process through electric arc heating. These electrodes are monitored by an extensive array of sensors that continuously collect operational parameters.

The sensor network captures multiple critical measurements for each electrode, including their vertical positioning, the status of upper and lower contact rings, surrounding air temperature, electrical current flow, and various other operational parameters. This multi-dimensional monitoring system ensures comprehensive coverage of the furnace's operational state and provides detailed insights into the smelting process dynamics.

Data acquisition was accomplished through AVEVA Historian (formerly known as Wonderware), an industrial-grade data collection and storage system. This platform is specifically designed for real-time process data management in industrial environments, ensuring high reliability and accuracy of the collected measurements. The system maintains a continuous record of sensor readings with precise timestamps, creating a detailed operational history of the furnace.

To prepare the data for analysis, structured queries were developed and executed using Microsoft SQL Server to extract the relevant sensor data from the AVEVA Historian database. The extraction process was carefully designed to maintain data integrity while converting the industrial time-series data into a format suitable for analytical processing. The final dataset was exported as a CSV (Comma-Separated Values) file, containing chronologically ordered time-series data that captures the complete operational profile of the thermal-ore furnace.

The resulting dataset represents a rich source of historical operational information, including both normal operating conditions and periods of equipment stress or failure. This comprehensive data collection provides the foundation for developing and validating predictive maintenance models, with the potential to identify patterns and anomalies that precede equipment failures or maintenance requirements.

\section{Literature Review}

\subsection*{1. Industry 4.0 and Smart Manufacturing}

Industry 4.0 represents a paradigm shift in manufacturing, characterized by the integration of cyber-physical systems, the Internet of Things (IoT), and advanced data analytics \cite{zhang-2021}. Zhang et al. \cite{zhang-2021} provide a comprehensive review of Industry 4.0 and its implementation, highlighting its potential to enhance efficiency and productivity in manufacturing.  The concept of smart manufacturing, a key component of Industry 4.0, leverages interconnected systems and data-driven decision-making to optimize production processes. Liu et al. \cite{liu-2023} delve into the IoT ecosystem for smart predictive maintenance (IoT-SPM) in manufacturing, emphasizing the multiview requirements and data quality crucial for effective implementation. Their evaluative study underscores the importance of a robust IoT infrastructure for realizing predictive maintenance capabilities.

Digital twins, virtual representations of physical assets, are also integral to smart manufacturing. Lattanzi et al. \cite{lattanzi-2021} review the concepts of digital twins in the context of smart manufacturing, exploring their practical industrial implementation. Digital twins facilitate real-time monitoring and simulation, enabling proactive maintenance and process optimization. Furthermore, the principles of Industry 4.0 extend to sustainability in manufacturing. Awasthi et al. \cite{awasthi-2021} discuss sustainable and smart metal forming manufacturing processes, indicating the broader impact of these technological advancements on environmental and economic aspects of production.

\subsection*{2. Equipment Sensors in Manufacturing Facilities}

Equipment sensors are fundamental to acquiring real-time data in manufacturing environments, enabling monitoring, control, and optimization of industrial processes. Jiang et al. \cite{jiang-2020} present a review on soft sensors, which are inferential sensors that utilize readily available process measurements to estimate difficult-to-measure variables. These sensors are crucial for enhancing process visibility and control.  For effective condition monitoring, robust data acquisition systems are essential. Toscani et al. \cite{toscani-2023} introduce a novel scalable digital data acquisition system designed for industrial condition monitoring, highlighting its potential for real-time data collection and analysis.

The data collected from equipment sensors, often in the form of multivariate time-series data, plays a critical role in detecting anomalies and predicting equipment failures. Nizam et al. \cite{nizam-2022} propose a real-time deep anomaly detection framework specifically for multivariate time-series data in industrial IoT settings. Their work demonstrates the application of deep learning for timely anomaly detection, which is crucial for preventing downtime and ensuring operational continuity. Pech et al. \cite{pech-2021} further emphasize the role of predictive maintenance and intelligent sensors in the smart factory, providing a review of how these technologies converge to create more efficient and resilient manufacturing systems.

\subsection*{3. Machine Learning in Industrial Applications}

Machine learning (ML) is at the core of analyzing sensor data and developing predictive models for industrial applications. Amer et al. \cite{amer-2023} discuss the application of machine learning methods for predictive maintenance, showcasing how ML algorithms can be trained to predict equipment failures based on sensor data.  Anomaly detection, a key application of ML in manufacturing, is further explored by Liu et al. \cite{liu-2021}. They propose an anomaly detection method on attributed networks using contrastive self-supervised learning, which can be adapted for identifying unusual patterns in sensor networks.

In the context of industrial soft sensors, Ou et al. \cite{ou-2022} introduce quality-driven regularization for deep learning networks. Their work focuses on enhancing the reliability and accuracy of soft sensors through advanced deep learning techniques.  Addressing the challenge of limited data in industrial settings, Zhou et al. \cite{zhou-2022} present a time series prediction method based on transfer learning. This approach is particularly relevant in manufacturing environments where historical failure data might be scarce, enabling more effective predictive modeling even with limited datasets.

\subsection*{4. Time Series Data Processing for Equipment Monitoring}

The data generated by equipment sensors is typically time-series data, requiring specialized processing techniques for effective analysis and prediction. Islam et al. \cite{islam-2024} introduce a novel probabilistic feature engineering approach, RKnD, for understanding time-series data, although their specific application is in driver behavior understanding, the principles of feature engineering are transferable to manufacturing sensor data.  Makridakis et al. \cite{makridakis-2022} provide a comprehensive comparison of statistical, machine learning, and deep learning forecasting methods for time series data. Their review offers insights into the strengths and weaknesses of different methods, guiding the selection of appropriate techniques for equipment monitoring.

Preprocessing sensor data to remove noise and enhance signal quality is crucial for accurate analysis. Alami and Belmajdoub \cite{alami-2024} discuss noise reduction techniques in sensor data management, although focused on ADAS sensors, the comparative analysis of methods is relevant for industrial sensor data as well.  Furthermore, understanding the context of the manufacturing process is important. Taskinen and Lindberg \cite{taskinen-2024} highlight the challenges facing non-ferrous metal production, providing a domain-specific perspective that can inform the development of sensor-based monitoring systems in metal smelting factories.

\subsection*{5. Predictive Maintenance in Metal Smelting Factories}

Predictive maintenance is a critical application of sensor-based monitoring and machine learning in industries like metal smelting. Olesen and Shaker \cite{olesen-2020} present a state-of-the-art review of predictive maintenance for pump systems and thermal power plants, outlining trends and challenges that are also pertinent to metal smelting factories which often involve similar equipment. Leukel et al. \cite{leukel-2021} systematically review the adoption of machine learning technology for failure prediction in industrial maintenance. Their findings are valuable for understanding the practical implementation and benefits of ML-based predictive maintenance strategies.

The economic evaluation of implementing artificial intelligence in manufacturing, including predictive maintenance, is also a key consideration. Chen et al. \cite{chen-2021} discuss the economic evaluation of energy efficiency and renewable energy technologies using artificial intelligence, providing a framework for assessing the financial viability of AI-driven solutions in industrial settings.

\subsection*{6. Challenges and Ethical Considerations in Industrial AI Deployment}

Deploying AI and machine learning models in industrial environments is not without challenges and ethical considerations. Khowaja et al. \cite{khowaja-2022} propose a two-tier framework for data and model security in industrial private AI, addressing the critical aspect of data privacy and security in interconnected manufacturing systems. Paleyes et al. \cite{paleyes-2022} provide a survey of case studies highlighting the challenges in deploying machine learning in real-world applications, emphasizing the practical hurdles that need to be overcome. Landers and Behrend \cite{landers-2022} discuss the ethical dimension, specifically focusing on auditing AI auditors and evaluating fairness and bias in high-stakes AI predictive models, raising important questions about the responsible and ethical deployment of AI in manufacturing.

\section{Analysis of Existing Systems}

\subsection{Traditional Rule-Based Systems}
Traditional Rule-Based Systems have been a cornerstone in industrial automation for decades. \cite{costa-2023} These systems rely on predefined rules to monitor and control processes, but they often lack the flexibility and adaptability required for modern manufacturing demands. Moreover, many traditional rule-based implementations are proprietary, not open source, and typically do not support on-premise deployment. This results in data being managed off-site, which raises significant concerns regarding data privacy and confidentiality.

\subsection{AWS Industrial Solutions}
AWS Industrial Solutions provide a broad array of cloud-based services designed for industrial applications, including real-time monitoring and predictive maintenance. \cite{aws-2025} Despite their advanced capabilities, these solutions are proprietary and not open source. Additionally, they are designed exclusively for cloud deployment, which limits the option for on-premise installations. This reliance on external cloud environments can compromise data privacy and confidentiality, as sensitive operational data must be transferred to and stored within third-party data centers.

\subsection{SAP Leonardo}
SAP Leonardo integrates innovative technologies such as IoT, machine learning, and big data analytics to enable smart manufacturing solutions. \cite{sap-2024} However, SAP Leonardo is a proprietary system and does not offer an open source alternative or on-premise deployment. This dependency on cloud-based services raises issues related to data security, privacy, and the confidentiality of sensitive information, as all data processing occurs off-premise.

\subsection{Google Cloud MDE \& Connect}
Google Cloud MDE \& Connect is designed to enhance industrial operations through cloud-based connectivity and data management solutions. \cite{rao-2024} Like other cloud-centric platforms, it is not open source and lacks support for on-premise deployment. The necessity to store and process data in Google’s cloud infrastructure can pose risks to data privacy and confidentiality, as the control over sensitive data is relinquished to a third-party provider.

\subsection{Nvidia Omniverse}
Nvidia Omniverse is a collaborative platform that facilitates real-time simulation and visualization for industrial applications. \cite{nvidia-2025} Although it offers state-of-the-art tools for digital transformation, Nvidia Omniverse is not an open source solution and does not support on-premise deployment. This reliance on a cloud-based environment means that proprietary data and simulation models are managed externally, potentially leading to concerns over data privacy and confidentiality.

