\chapter{Definitions}
\label{chap:definitions}
\setlength{\parskip}{1em}

\paragraph{Python} Python is a high-level, interpreted programming language widely used in scientific sphere for data science, machine learning, and scientific computing. Its simplicity and extensive ecosystem of libraries made it easy choice for data analysis and processing.

\paragraph{UV} an Python package and project manager, written in Rust. It is fast to manage and deploy compared to other solutions, which makes it suitable for easy to deploy systems.

\paragraph{CUDA} Compute Unified Device Architecture (CUDA) is a computing platform and programming model developed by NVIDIA. It uses parallel computation, which accelerates processing and allows development to utilize GPU acceleration for deep learning, numerical simulations, and large-scale computations.

\paragraph{Linux} Linux is an open-source operating system kernel. It is known for its stability, security, and flexibility. CUDA and Python works best on Linux.

\paragraph{Visual Studio Code} Visual Studio Code is an code editor developed by Microsoft. It is extensible with plugins and works reliably in Linux. 

\paragraph{Jupyter} Jupyter is an application that allows to write Python code alongside Markdown documentations. It works with Python environments out of the box and decreases complexity of the code base. It works well in Visual Studio Code editor.

\paragraph{TensorFlow} TensorFlow is an open-source machine learning framework developed by Google. It provides tools for building and deploying deep learning models efficiently, supporting both CPU and GPU acceleration.

\paragraph{Keras} Keras is a high-level deep learning API that runs on top of TensorFlow. It simplifies the process of building and training neural networks by providing an intuitive and user-friendly model development interface.

\paragraph{Matplotlib} Matplotlib is a Python library for creating static, animated, and interactive visualizations. It is commonly used for plotting data in scientific computing and machine learning.

\paragraph{Scikit-learn} Scikit-learn is an open-source Python library for machine learning. It provides simple and efficient tools for data mining and analysis, including classification, regression, clustering, and dimensionality reduction. It also makes scaler configuration for model inputs simple.

\paragraph{Pandas} Pandas is a Python library used for data manipulation and analysis. It offers powerful data structures like DataFrames and Series, facilitating efficient data handling and preprocessing.

