\chapter{Analysis of Existing Systems}
\label{chap:existing_systems}
\setlength{\parskip}{1em}

\subsection{Traditional Rule-Based Systems}
Traditional Rule-Based Systems have been a cornerstone in industrial automation for decades. These systems rely on predefined rules to monitor and control processes, but they often lack the flexibility and adaptability required for modern manufacturing demands. Moreover, many traditional rule-based implementations are proprietary, not open source, and typically do not support on-premise deployment. This results in data being managed off-site, which raises significant concerns regarding data privacy and confidentiality.

\subsection{AWS Industrial Solutions}
AWS Industrial Solutions provide a broad array of cloud-based services designed for industrial applications, including real-time monitoring and predictive maintenance. Despite their advanced capabilities, these solutions are proprietary and not open source. Additionally, they are designed exclusively for cloud deployment, which limits the option for on-premise installations. This reliance on external cloud environments can compromise data privacy and confidentiality, as sensitive operational data must be transferred to and stored within third-party data centers.

\subsection{SAP Leonardo}
SAP Leonardo integrates innovative technologies such as IoT, machine learning, and big data analytics to enable smart manufacturing solutions. However, SAP Leonardo is a proprietary system and does not offer an open source alternative or on-premise deployment. This dependency on cloud-based services raises issues related to data security, privacy, and the confidentiality of sensitive information, as all data processing occurs off-premise.

\subsection{Google Cloud MDE \& Connect}
Google Cloud MDE \& Connect is designed to enhance industrial operations through cloud-based connectivity and data management solutions. Like other cloud-centric platforms, it is not open source and lacks support for on-premise deployment. The necessity to store and process data in Google’s cloud infrastructure can pose risks to data privacy and confidentiality, as the control over sensitive data is relinquished to a third-party provider.

\subsection{Nvidia Omniverse}
Nvidia Omniverse is a collaborative platform that facilitates real-time simulation and visualization for industrial applications. Although it offers state-of-the-art tools for digital transformation, Nvidia Omniverse is not an open source solution and does not support on-premise deployment. This reliance on a cloud-based environment means that proprietary data and simulation models are managed externally, potentially leading to concerns over data privacy and confidentiality.